Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-10-16 manuscript/text_reuse.tex
added a bit to the introduction

\subsection{Tasks}
\begin{itemize}
\item Write paragraph about how it would be great if text-reuse could be used to classify policy overlap (BD)
\item Write paragraph on why this is not easy (FL)
\item Summarize what we do to solve problem and validate (FL)
\end{itemize}

...

@@

\subsection{Tasks}
\begin{itemize}
\item Scrape Google urls for NCSL tables (FL)
\item Extract state  \& bill \# from tables (FL)
\end{itemize}

>>>>

\subsection{Tasks}
\begin{itemize}
\item Write paragraph about how it would be great if text-reuse could be used to classify policy overlap (BD)
\item Write paragraph on why this is not easy (FL)
\end{itemize}
How ever, it is not clear, how well text reuse is suited to to detect real
policy diffusion. There are several complications that we are addressing in this
paper. First, every bill has procedural content that is not related to the
policy content of the bill. Since every state legislature has a set of such
standard or boiler plate text in each bill, there will be significant text reuse
between bills in the same state and possibly also between bills from different
states. Second, it is not obvious how much text reuse will mean substantive
policy overlap. Given that each bill pair has a continuous proportion of
overlapping text, setting the threshold too low might mean to classify bills as
equivalent that are only in the same policy area, or are on a similar issue, but
are opposed in content. On the other hand, setting the threshold too high could
mean overlooking equivalent bills because of small insignificant changes to the
text.

In this paper we address these issues and evaluate how much policy overlap can
be detected using text reuse measures. Following Wilkerson et al. (2015) we use
supervised machine learning to separate boiler plate from substantive text. We
further more use an original data set on policy diffusion to evaluate how much
equivalent policy can be detected using measures of text reuse. Using the system
developed by Burges et al. (2015) we calculate text reuse scores for all pairs
of bills in our dataset. We then use these scores in a model that classifies
bills as equivalent and evaluate its performance with the validation data set.

This work has several important implications. First, it allows us to estimate,
how policies are transferred between states. Do state legislators work mainly
from templates from other states or interest groups, or to what extent do
legislators draft their own bill text. Furthermore, text reuse is a relatively
simple metric to calculate for large amounts of text. Previous scholars of
policy diffusion mainly relied on case studies or manually coded data sets of
policy diffusion in few policy areas. If working copying text forms a
significant portion of how legislators adopt policies from other states, text
reuse can be used to easily gather comprehensive data sets on policy diffusion.

[This might be overlapping a bit with your part]

@@

\subsection{Tasks}
\begin{itemize}
\item Scrape Google urls for NCSL tables (
\item Extract state  \& bill \# from tables (FL)
\end{itemize}
